A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-15 doc/draft-01-stokes/03analysis.tex
update sections, minor edits

\begin{definition}[Interior impedance problem]
\label{def:int_imp}
  Let $\bh \in C(\Omega)$ be given and suppose 
  $\eta \in \mathbb{C}$ with $\Re{(\eta)},\Im{(\eta)}>0$. 
  Find $(\bu,p) \in A(\Omega)$  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_interior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
    \bt - i \eta \bu &= \bh \quad \bx \in \Gamma \, .
  \end{aligned}
  \end{equation}
\end{definition}

@@

\begin{definition}[Exterior impedance problem]
  \label{def:imp_exterior}  
  Let $\bh \in C(\Gamma)$ be given and suppose that
  $\eta \in \mathbb{C}$ with $\Re{(\eta)},\Im{(\eta)} >0$. 
  Find $(\bu,p) \in A(E)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:imp_exterior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
    \bt + i\eta \bu &= \bh \quad \bx \in \Gamma \, ,
  \end{aligned}
  \end{equation}
  and $(\bu,p)$ satisfies the radiation condition in
  \cref{def:radcond}.
\end{definition}

>>>>

\begin{definition}[Interior impedance problem]
\label{def:int_imp}
  Let $\bh \in C(\Omega)$ be given and suppose 
  $\eta \in \mathbb{C}$ with $\Re{(\eta)} >0$ and $\Im{(\eta)}\ge 0$. 
  Find $(\bu,p) \in A(\Omega)$  such that
  \begin{equation}
  \begin{aligned} \label{eq:neu_interior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in \Omega \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in \Omega \, ,  \\
    \bt - i \eta \bu &= \bh \quad \bx \in \Gamma \, .
  \end{aligned}
  \end{equation}
\end{definition}

@@

\begin{definition}[Exterior impedance problem]
  \label{def:imp_exterior}  
  Let $\bh \in C(\Gamma)$ be given and suppose that
  $\eta \in \mathbb{C}$ with $\Re{(\eta)} > 0$ and $\Im{(\eta)} \ge 0$. 
  Find $(\bu,p) \in A(E)$
  such that
  \begin{equation}
  \begin{aligned} \label{eq:imp_exterior}
    \Delta \bu + k^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
    \nabla \cdot \bu &= 0 \quad \bx \in E \, ,  \\
    \bt + i\eta \bu &= \bh \quad \bx \in \Gamma \, ,
  \end{aligned}
  \end{equation}
  and $(\bu,p)$ satisfies the radiation condition in
  \cref{def:radcond}.
\end{definition}

### 2019-04-15 doc/draft-01-stokes/04numerical.tex
update numerical section and appendix
update sections, minor edits

The integral kernels of the single and
double layer potentials have weak
singularities of the form $r^p\log r$
which require special quadrature rules to
achieve high-order accuracy.
%
In the examples below, we use generalized
Gaussian quadrature (GGQ)~\cite{bremer2010}.
%
To demonstrate the idea, we consider
evaluating the convolution of a kernel
$K$ with a density $\sigma$
at the boundary node $\xx_j(t_l)$.
%
GGQ is a Nystr\"{o}m-type discretization ---
the density is approximated 
by its values at the discretization nodes,
which we denote by
$\sigma_{qp} := \sigma(\xx_q(t_p))$.
%
The basis of a GGQ rule is a set of 
support nodes and weights for the
contribution to the integral from the
``self'' panel (panel $j$) and the adjacent
panels (with index in $A(j)$).
%

@@

We now consider the multiply-connected domain in
\cref{subfig:many_inclusions_bdry}.
% 
The domain is defined by a smooth rectangular region
of width 3 and height 2,
with an array of randomly rotated ``starfish'' shapes
removed. 
%
Such shapes are of interest in
materials design and micro-fluidics \note{cite}.
%
We compute the eigenfunctions corresponding to
eigenvalues $k^2$ with $k$ in the range
$3 \leq k \leq 9$ (this range includes the smallest
eigenvalue).

@@

We compute the roots of these Chebyshev interpolants
and apply the post-processing described above.
%
There were 103 total roots: 21 were removed because
the imaginary part was too large and 6 pairs were found
with values within $\sqrt{\epscheb}$ of each other.
%
For these 6 pairs, none represented two distinct
eigenvalues or a double root.
%
This leaves 76 roots in the range $0\leq k \leq 9$.
%
We plot the smallest singular value of
$\cI^N-\cDk^N-2i\cSk^N-2\cW^N$ for each of these roots in
\cref{subfig:many_inclusions_sings}
and plot the vorticity of the eigenfunctions
in \cref{fig:many_inclusions_gallery}.
%
In the vorticity plots, we observe a different type of
localization property than that seen in the barbell,
with many of the eigenfunctions
approximately supported in a small, connected subset
of the domain. This is consistent with other studies
\note{cite}

>>>>

The integral kernels of the single and
double layer potentials have weak
singularities of the form $|\xx-\yy|^p\log |\xx-\yy|$
for some $p \in \N_0$, which require special
quadrature rules to achieve high-order accuracy.
%
In the examples below, we use generalized
Gaussian quadrature (GGQ)~\cite{bremer2010}.
%
To demonstrate the idea, we consider
evaluating the convolution of a kernel
$K$ with a density $\sigma$
at the boundary node $\xx_j(t_l)$.
%
GGQ is a Nystr\"{o}m-type discretization ---
the density is approximated 
by its values at the discretization nodes,
which we denote by
$\sigma_{qp} := \sigma(\xx_q(t_p))$.
%
The basis of a GGQ rule is a set of 
support nodes and weights for the
contribution to the integral from the
``self'' panel (panel $j$) and the adjacent
panels (with index in $A(j)$).
%

@@

We now consider the multiply-connected domain in
\cref{subfig:many_inclusions_bdry}.
% 
The domain is defined by a smooth rectangular region
of width 3 and height 2,
with an array of randomly rotated ``starfish'' shapes
removed. 
%
Such shapes are of interest in
materials design, see, for instance, \cite{overvelde2012compaction}.
%
We compute the eigenfunctions corresponding to
eigenvalues $k^2$ with $k$ in the range
$3 \leq k \leq 9$ (this range includes the smallest
eigenvalue).

@@

We compute the roots of these Chebyshev interpolants
and apply the post-processing described above.
%
There were 103 total roots: 21 were removed because
the imaginary part was too large and 6 pairs were found
with values within $\sqrt{\epscheb}$ of each other.
%
For these 6 pairs, none represented two distinct
eigenvalues or a double root.
%
This leaves 76 roots in the range $0\leq k \leq 9$.
%
We plot the smallest singular value of
$\cI^N-\cDk^N-2i\cSk^N-2\cW^N$ for each of these roots in
\cref{subfig:many_inclusions_sings}
and plot the vorticity of the eigenfunctions
in \cref{fig:many_inclusions_gallery}.
%
In the vorticity plots, we observe a different type of
localization property than that seen in the barbell,
with many of the eigenfunctions
approximately supported in a small, connected subset
of the domain. This is consistent with other studies
\cite{filoche2009strong,lindsay2018boundary}.
